### 2022-06-15 main/chapter_2ljets.tex
improve numerical simp paragraph
yet another internal doc sentence rearrangement

Furthermore, simplicity encourages interpretability and trust.
A selection at $100\,\eV[G]$ may be slightly outperformed in precision by one
at $100.314\,\eV[G]$, but the former is preferable --- it is easily
communicated and perhaps understood or reproduced by readers.
The latter could be overly tuned, perhaps by a learning algorithm, to specific
simulations.
Perhaps it cut out a highly weighted sample which, although annoying, was an
honest representation of our modelling.
Denying ourselves the ability to over-fit simulations keeps us honest.

Numerical simplicity is valuable.
I stated this as a design goal in internal documentation, but that statement was
removed after one \atlas\ author commented
``maybe this paragraph is a little
\emph{too honest}? (The `numerical simplicity' bit)''
(emphasis added)~\cite{comment2020toohonest}.

>>>>

Furthermore, simplicity encourages interpretability and trust.
A selection at $100\,\eV[G]$ may be slightly outperformed in precision by one
at $100.314\,\eV[G]$, but the former is preferable --- it is easily
communicated and perhaps understood or reproduced by readers.
The latter could be overly tuned, perhaps by a learning algorithm, to specific
simulations.
Perhaps it cut out a highly weighted sample which, although annoying, was an
honest representation of our modelling.
Restricting ourselves to round numbers not only clarifies our communications,
but keeps us honest by denying ourselves the ability to over-fit simulations.

Numerical simplicity is valuable.
In internal documentation, I stated that it was a motivator behind the design,
but that statement was removed after one \atlas\ author commented:
``maybe this paragraph is a little
\emph{too honest}? (The `numerical simplicity' bit)''
(emphasis added)~\cite{comment2020toohonest}.
